\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-30 latex/paper_sensores/paper.tex
varias correcciones, quedo listo

\begin{abstract}
%\boldmath
This paper presents a fast and low cost way to calibrate different inertial measurement sensors. In particular we present the calibration of an accelerometer and a gyroscope using nonlinear least squares. A model of the sensors is presented based on the main errors that MEMS devices present, a calibration method is proposed for the static parameters of the model. Finally a temperature adjust is made.  
% -cambio-
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\section{Introduction}
The development of the Micro-electromechanical Systems (MEMS) technology has allowed to manufacture many low-cost chip-sensors, such as accelerometers, gyroscopes and magnetometers. Those chips have been adopted in many applications, for instance Inertial Navigation Systems  (INS) \cite{bib:un_puto_nuevo}. However this sensors have many error sources, thus they must be calibrated before being used and they should be re-calibrated periodically for any precision application. The different sources of error will be analysed in more detail in section \refp{sec:modelo} and the implications of those errors will be derived.\\

The calibration proposed in this work is tested on a 3-axis accelerometer \emph{ADXL345} of \emph{Analog Devices} and a 3-axis gyroscope \emph{ITG-3200} of \emph{InvenSense}, yet the model developed and the methodology can be used in other devices because the model is based on common characteristics of MEMS sensors. The sensors named before are included in a Inertial Measurement Unit(IMU): The Mongoose (figure \refp{fig:mongoose}). \\

@@

We take in consideration a fact that is not usually taken into account in the literature (see \cite{bib:calib_imu}, \cite{bib:kalman}, \cite{bib:calib_imu_dos}): the measures given by this sensors are not independent of the temperature. Previous works \cite{bib:ultimo_tio}, considered time varying drifts not depending on temperature but with known dependency on time, and neglecting axis non-orthogonality. Many devices that uses MEMS sensors need to work properly in a wide temperature range. In other cases, the temperature in operation of the system is different(for instance due to Joule Effect of the wires near the sensors) than the ambiance temperature in which the sensor was calibrated. Therefore a temperature adjust must be made.

@@

As it was stated before, there exist many error sources in MEMS devices. In \cite{bib:calib_imu} two of this sources are mentioned: the nonlinear response of the sensors and the non-orthogonality of the axis of the sensor. In addition we can observe also that it exist an electric noise in the measures (Figure \ref{fig:noise}) and a dependence of the temperature.\\
\vspace{-10pt}
\begin{figure}[h!]
  \centering
  \subfloat[Accelerometer data $\hat{k}$]{\label{fig:angulos_1}
  		\includegraphics[width=1\columnwidth]
  			{./pics_paper/acc_noise.pdf}}\\[-5pt]
  			\vspace{-5pt}
  \subfloat[Gyroscope data $\hat{j}$]{\label{fig:angulos_2} 
  		\includegraphics[width=1\columnwidth]
  			{./pics_paper/gyro_noise.pdf}}
  \caption{\textbf{Noise -} Measures from accelerometer and gyroscope in static equilibrium.}
  \label{fig:noise}
\end{figure}

@@

In Figure \refp{fig:noise} we can observe that the electrical noise of the devices is typically 3 LSB (Least Significant Bit) peak to peak, which (according to the datasheets \cite{bib:acc_data, bib:gyro_data}) correspond to $11.7 mg$ and $0.21 ^{\circ}/s $. The error is not biased, thus, we not need to consider it, because many samples are used in the procedure and the effect vanishes.\\

Based on the assumption that both sensors have a linear response and considering the non-orthogonality of the axis of the devices we are going to present a standard model for both sensors (see \cite{bib:calib_imu}, \cite{bib:kalman}, \cite{bib:calib_imu_dos}).

\subsection{Accelerometer}
Due to construction issues the sensitivity axis of the device are generally not orthogonal. Lets define a platform system as shown in Figure \refp{fig:mongoose}. Let $\mathbf{a}^a$ be the true acceleration (meaning the theoretical acceleration measured in $ms^{-2}$) expressed in the sensitivity axis of the accelerometer and let $\mathbf{a}^p$ be the theoretical true acceleration (also measured in $ms^{-2}$) expressed in the platform system. The two acceleration vectors are related according to equation \refp{eq:nonorto}:
\begin{equation}
\mathbf{a}^p = \mathbf{T}_a^p\mathbf{a}^a, \; \mathbf{T}_a^p = \left(\begin{array}{ccc}
1 & - \alpha_{yz} & \alpha_{zy}\\
\alpha_{xz} & 1 & - \alpha_{zx}\\
-\alpha_{xy} & \alpha_{yx} & 1
\end{array}\right)
\label{eq:nonorto}
\end{equation}
In equation \refp{eq:nonorto}, scalars $\alpha_{ij}$ represents the rotation of the $i-th$ sensitivity axis of the accelerometer over the $j-th$ axis of the platform system. In Figure \refp{fig:nonorto}\footnote{Figure taken form \cite{bib:calib_imu}} this relation can be observed graphically. Since those errors are due to the manufacturing process we will assume that they will remain constant long enough.

@@

As it was stated before, a linear model between the acceleration measured in the sensitivity axis and the true acceleration in the same system is considered. Thus we have:
\begin{equation}
\tilde{\mathbf{a}}^a = \mathbf{K}_a\mathbf{a}^a + \mathbf{b}_a
\label{eq:modlineal}
\end{equation}
In equation \refp{eq:modlineal}, $\tilde{\mathbf{a}}^a$ is the measure obtained by the accelerometer (measured in bits), $\mathbf{K}_a$ is a diagonal matrix that represents the sensitivity of each axis and $\mathbf{b}_a$ is a vector that represent the bias of each axis. Those parameters may variate as the temperature changes. However, constant temperature is considered. Using equations \refp{eq:nonorto} and \refp{eq:modlineal} we can establish a model of the accelerometer:

@@

\subsection{Gyroscope}
The error sources consider in the case of the gyroscope are the same that we developed for the accelerometer. Thus, we are going to consider the same model:

@@

\section{Calibration method proposed}
The problem of calibration is to establish the values for the unknown parameters of the model that adjust ``the better'' a certain set of data. This criterion will be defined in Section \refp{sec:param}.

@@

Let $\boldsymbol{\theta}_s$ (where the subindex $s$ refers to a sensor) be the parameter vector of a certain sensor. We can define this vector as:
\begin{equation}
\boldsymbol{\theta} = [k_{sx},k_{sy},k_{sy},b_{sx},b_{sy},b_{sy}, \alpha_{sxy},\alpha_{sxz},\alpha_{syx},\alpha_{syz},\alpha_{szx},\alpha_{szy}]^T
\label{eq:theta}
\end{equation}

@@

As adjust criterion we choose to minimize the sum of the squares of the norms of the differences between true acceleration and measured acceleration. This problem can be written as follows:

\begin{equation}
\min_{\boldsymbol{\theta}} \sum_{i = 1}^M ||\mathbf{s}_i^p - \mathbf{T}_s^p(\mathbf{K_s})^{-1}(\tilde{\mathbf{s}}_i^s-\mathbf{b}_s) ||^2
\label{eq:calib_problem}
\end{equation}

@@

It is important to consider that the minimize function will generally have more than one local minimum. To ensure that the solution obtained is the desired one, the seed for the algorithm must be carefully chosen. Thus, datasheet values of the parameters are chosen as seed for the optimization.

Typically we will choose a vector $\boldsymbol{\theta}_0$ that is close to the values of the unknown parameters. Even if we do not know the exact value of the model's parameters, the datasheet of the different sensors can give us a very good clue about those values.\\

\subsubsection{Accelerometer}
\label{subsec:acc}
Since an accelerometer measures the acceleration in a free fall referential, in static equilibrium it will measure an acceleration that has as norm the gravitational constant of the  earth ($g = 9.81ms^{-2}$), its direction is collinear with the line defined by the position of the accelerometer and the center of the earth and its sense is from the center of the earth towards the position of the accelerometer, meaning ``up''. This allows to have an exact expression for the acceleration, the procedure used consist in measureing magnitude with different orientations of the acceleration and then solve the problem stated in equation \refp{eq:calib_problem}.\\

The 27 measures made were the following:
\begin{itemize}
\item Starting position: $x$ axis pointing ``down'': 9 measures were made combining two rotations. First, rotating around the $z$ axis $\theta =0^\circ, 10^\circ, 20^\circ, 30^\circ, 45^\circ$. Then, for each angle defined(except for $\theta = 0^\circ$), two measures were made rotating around the $x$ axis $\psi = 0^\circ, -45^\circ$. This set of measures can be expressed in the following way:
\begin{scriptsize}
\begin{equation}
\mathbf{a}^p = \left(\begin{array}{ccc}
1 & 0 & 0\\
0 & \cos \psi & \sin \psi \\
0 & -\sin \psi & \cos \psi
\end{array}\right)\left(\begin{array}{ccc}
\cos \theta & \sin \theta & 0\\
-\sin \theta & \cos \theta & 0\\
0 & 0 & 1
\end{array}\right)\left(\begin{array}{c}
-g\\
0\\
0
\end{array}\right)
\label{eq:acc_x}
\end{equation}
\end{scriptsize}

\item Starting position: $y$ axis pointing ``up'': 9 measures were made combining two rotations. First, rotating around the $x$ axis $\psi =0^\circ, 10^\circ, 20^\circ, 30^\circ, 45^\circ$. Then, for each angle defined(except for $\theta = 0^\circ$), two measures were made rotating around the $y$ axis $\varphi = 0^\circ, 45^\circ$.

@@

\item Starting position: $z$ axis pointing ``up'': 9 measures were made combining two rotations. First, rotating around the $y$ axis: $\phi =0^\circ, -10^\circ, -20^\circ, -30^\circ, -45^\circ$. Then, for each angle defined(except for $\phi = 0^\circ$), two measures were made rotating around the $z$ axis $\theta = 0^\circ, 45^\circ$.   \end{itemize}

@@

First of all, we attached the platform to a wooden cube. This allows us to perform $90^\circ$ rotations, thus if we had an horizontal surface we can take measures with the gravity vector aligned to any of three axis. The horizontal surface was assured using a three leg adjustable table (see Figure \refp{fig:mesa}). In addition this table allows us to perform rotations of known angles using a scaled semicircle and a pendulum as it is shown also in Figure \refp{fig:mesa}. The rotations over the second axis were made using a carpenter's square, therefore we have a proper $45^\circ$ rotation.\\

@@

@@

In this work we also propose to implement a temperature adjustment. The sensors are exposed to the operating temperature of the system, and it is very common that this temperature is different from the calibration temperature. The thermometer used in this work is the internal thermometer of the IMU, which indicates very precisely the operating temperature of the sensor. Sensors based in MEMS technology are sensitive to such variations. The variation of the measures is critical in some applications. In INS two of the Euler angles are usually obtained from the accelerometer, therefore if the measures are not certain the stability of the system cannot be guaranteed.\\

@@

The conclusion of this sum up information is that the variations of the temperature do not produce main changes on the gains of the sensors, yet the offsets are modified. Thus, we are going to consider the following temperature adjust:

@@

In equation \refp{eq:temp} $\mathbf{b}_{s0}$ is the offset vector obtained in the static calibration, $T_0$ is the ambiance temperature in that calibration, $T$ is the working temperature of the system and $\boldsymbol{\alpha}_s$ is the parameter that we need to know to complete the process.\\

@@

\begin{equation}
\min_{\boldsymbol{\alpha}_s} = \sum_{k=1}^N ||\mathbf{s}_i^p - \mathbf{T}_{s0}^p(\mathbf{K_{s0}})^{-1}(\tilde{\mathbf{s}}_i^s-\mathbf{b}_s(T))||^2 
\label{eq:calib_temp}
\end{equation}

In equation \refp{eq:calib_temp}, $N = 22740$\footnote{This number is not needed to be this big, yet all the data of the cooling process was used (see figure \ref{fig:bajada}).} is the number of samples took, $\mathbf{T}_{s0}^p$, $\mathbf{K_{s0}}$ are the matrix obtained in the static parameter calibration (ambiance temperature) and $\mathbf{b}_s(T)$ is the vector defined in \refp{eq:temp}. This last vector includes the variable that we want to estimate.\\

@@

It is interesting to compare the values obtained with the theoretical values of each parameter. As we can see, comparing the vector obtained with the seed, the values of the gains and the rotations are similar to what is declared in the datasheets. Furthermore, the offset values are also consistant with the information of the datasheet, yet this is not a straightforward conclusion, thus we present the following analyisis. In \cite{bib:acc_data} is declared that the $0g$ output is $\pm 150 mg$ for axes $x$ and $y$ and $\pm 250mg$ for axis $z$. This correspond to offsets of $39$ bits maximum for $x$ and $y$, and $64$ for $z$. Therefore, we can conclude that the results obtained are consistent with what is declared in the datasheets.

@@

The mean error obtained correspond to less that a bit of error and the standard deviation to a bit and a half. Therefore we can conlude that a very good calibration has been achieved for the static parameters of the accelerometer.\\

@@

For the calibration there were used 1934 samples, taken in about 20 seconds.\\

>>>>

\begin{abstract}
%\boldmath
This paper presents a fast and low cost way to calibrate different inertial measurement sensors. In particular the calibration of an accelerometer and a gyroscope using nonlinear least squares is presented. A model of the sensors which includes the main errors that MEMS devices present is used. A calibration method is proposed for estimating the static parameters of the model and a temperature adjustment is proposed and implemented.

\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

\section{Introduction}
The development of the Micro-electromechanical Systems (MEMS) technology has allowed to manufacture many low-cost chip-sensors, such as accelerometers, gyroscopes and magnetometers. Those chips have been adopted in many applications, for instance Inertial Navigation Systems (INS) \cite{bib:un_puto_nuevo}. However this sensors have many error sources, thus they must be calibrated before being used and they should be re-calibrated periodically for any precision application. The different sources of error are analyzed in more detail in section \refp{sec:modelo} and the implications of those errors are derived.\\

The calibration proposed in this work is tested on a 3-axis accelerometer \emph{ADXL345} of \emph{Analog Devices} and a 3-axis gyroscope \emph{ITG-3200} of \emph{InvenSense}, yet the model developed and the methodology can be used in other devices because the model is based on common characteristics of MEMS sensors. The sensors named before are included in a Inertial Measurement Unit (IMU): The Mongoose (figure \refp{fig:mongoose}). \\

@@

A fact that is not usually taken into account in the literature (see \cite{bib:calib_imu}, \cite{bib:kalman}, \cite{bib:calib_imu_dos}) is taken into consideration: the measures given by this sensors are not independent of the temperature. Previous works \cite{bib:ultimo_tio}, considered time varying drifts not depending on temperature but with known dependency on time, and neglecting axis non-orthogonality. Many devices that uses MEMS sensors need to work properly in a wide temperature range. In other cases, the temperature in operation of the system is different (e. g. due to Joule Effect, close drivers, etc.) than the ambiance temperature in which the sensor was calibrated. Therefore a temperature adjust must be made.

@@

As it was stated before, there exist many error sources in MEMS devices. In \cite{bib:calib_imu} two of this sources are mentioned: the nonlinear response of the sensors and the non-orthogonality of the axis of the sensor. In addition, an electric noise (Figure \ref{fig:noise}) in the measures and a dependence of the temperature can be observed.\\
\vspace{-10pt}
\begin{figure}[h!]
  \centering
  \subfloat[Accelerometer data $\hat{k}$]{\label{fig:angulos_1}
  		\includegraphics[width=1\columnwidth]
  			{./pics_paper/acc_noise.pdf}}\\[-5pt]
  			\vspace{-5pt}
  \subfloat[Gyroscope data $\hat{j}$]{\label{fig:angulos_2} 
  		\includegraphics[width=1\columnwidth]
  			{./pics_paper/gyro_noise.pdf}}
  \caption{\textbf{Noise -} Measures from accelerometer and gyroscope in static equilibrium.}
  \label{fig:noise}
\end{figure}

@@

In Figure \refp{fig:noise} can be observed that the electrical noise of the devices is typically 3 LSB (Least Significant Bit) peak to peak, which (according to the datasheets \cite{bib:acc_data, bib:gyro_data}) correspond to $11.7 mg$ and $0.21 ^{\circ}/s $. The error is not biased, thus, it is not needed to be considered because many samples are used in the procedure and the effect vanishes.\\

Based on the assumption that both sensors have a linear response and considering the non-orthogonality of the axis of the devices, a standard model for both sensors is presented (see \cite{bib:calib_imu}, \cite{bib:kalman}, \cite{bib:calib_imu_dos}).

\subsection{Accelerometer}
Due to construction issues the sensitivity axis of the device are generally not orthogonal. Lets define a platform system as shown in Figure \refp{fig:mongoose}. Let $\mathbf{a}^a$ be the true acceleration (meaning the theoretical acceleration measured in $ms^{-2}$) expressed in the sensitivity axis of the accelerometer and let $\mathbf{a}^p$ be the theoretical true acceleration (also measured in $ms^{-2}$) expressed in the platform system. The two acceleration vectors are related according to equation \refp{eq:nonorto}:
\begin{equation}
\mathbf{a}^p = \mathbf{T}_a^p\mathbf{a}^a, \; \mathbf{T}_a^p = \left(\begin{array}{ccc}
1 & - \alpha_{yz} & \alpha_{zy}\\
\alpha_{xz} & 1 & - \alpha_{zx}\\
-\alpha_{xy} & \alpha_{yx} & 1
\end{array}\right)
\label{eq:nonorto}
\end{equation}
In equation \refp{eq:nonorto}, scalars $\alpha_{ij}$ represents the rotation of the $i-th$ sensitivity axis of the accelerometer over the $j-th$ axis of the platform system. In Figure \refp{fig:nonorto}\footnote{Figure taken form \cite{bib:calib_imu}} this relation can be observed graphically. Since those errors are due to the manufacturing process, they are assumed to remain constant long enough.

@@

As it was stated before, a linear model between the acceleration measured in the sensitivity axis and the true acceleration in the same system is considered. Thus:
\begin{equation}
\tilde{\mathbf{a}}^a = \mathbf{K}_a\mathbf{a}^a + \mathbf{b}_a
\label{eq:modlineal}
\end{equation}
In equation \refp{eq:modlineal}, $\tilde{\mathbf{a}}^a$ is the measure obtained by the accelerometer (measured in bits), $\mathbf{K}_a$ is a diagonal matrix that represents the sensitivity of each axis and $\mathbf{b}_a$ is a vector that represent the bias of each axis. Those parameters may variate as the temperature changes. However, constant temperature is considered. Using equations \refp{eq:nonorto} and \refp{eq:modlineal} a model of the accelerometer can be established:

@@

\subsection{Gyroscope}
The error sources considered in this case are the same as those considered for the accelerometer. Thus, the same model is considered:

@@

\section{Calibration method proposed}
The problem of calibration is to establish the values for the unknown parameters of the model that adjust ``the better'' a certain set of data. This criterion is defined in Section \refp{sec:param}.

@@

Let $\boldsymbol{\theta}_s$ (where the subindex $s$ refers to a sensor) be the parameter vector of a certain sensor. This vector can be defined as:
\begin{eqnarray}
\boldsymbol{\theta} &=& [k_{sx},k_{sy},k_{sy},b_{sx},b_{sy},b_{sy},\\ \nonumber
&&\alpha_{sxy},\alpha_{sxz},\alpha_{syx},\alpha_{syz},\alpha_{szx},\alpha_{szy}]^T
\label{eq:theta}
\end{eqnarray}

@@

The chosen criterion is to minimize the sum of the squares of the norms of the differences between true acceleration and measured acceleration. This problem can be written as follows:

\begin{equation}
\boldsymbol{\theta} = \arg \min_{\boldsymbol{\theta}} \lbrace \sum_{i = 1}^M ||\mathbf{s}_i^p - \mathbf{T}_s^p(\mathbf{K_s})^{-1}(\tilde{\mathbf{s}}_i^s-\mathbf{b}_s) ||^2 \rbrace
\label{eq:calib_problem}
\end{equation}

@@

It is important to consider that the minimize function may have more than one local minimum. To ensure that the solution obtained is the desired one, the seed for the algorithm must be carefully chosen. Datasheet values of the parameters are chosen as seed for the optimization.

\subsubsection{Accelerometer}
\label{subsec:acc}
Since an accelerometer measures the acceleration in a free fall referential, in static equilibrium it measures an acceleration that has as norm the gravitational constant of the  earth ($g = 9.81ms^{-2}$), its direction is collinear with the line defined by the position of the accelerometer and the center of the earth and its sense is from the center of the earth towards the position of the accelerometer, meaning ``up''. This allows to have an exact expression for the acceleration, the procedure used consists in measuring magnitude with different orientations of the acceleration and then solve the problem stated in equation \refp{eq:calib_problem}.\\

The 27 measures made were the following:
\begin{itemize}
\item Starting position: $x$ axis pointing ``down'': 9 measures were made combining two rotations. First, rotating around the $z$ axis $\theta =0^\circ, 10^\circ, 20^\circ, 30^\circ, 45^\circ$. Then, for each angle defined (except for $\theta = 0^\circ$), two measures were made rotating around the $x$ axis $\psi = 0^\circ, -45^\circ$. This set of measures can be expressed in the following way:
\end{itemize}

\begin{scriptsize}
\begin{equation}
\mathbf{a}^p = \left(\begin{array}{ccc}
1 & 0 & 0\\
0 & \cos \psi & \sin \psi \\
0 & -\sin \psi & \cos \psi
\end{array}\right)\left(\begin{array}{ccc}
\cos \theta & \sin \theta & 0\\
-\sin \theta & \cos \theta & 0\\
0 & 0 & 1
\end{array}\right)\left(\begin{array}{c}
-g\\
0\\
0
\end{array}\right)
\label{eq:acc_x}
\end{equation}
\end{scriptsize}

\begin{itemize}
\item Starting position: $y$ axis pointing ``up'': 9 measures were made combining two rotations. First, rotating around the $x$ axis $\psi =0^\circ, 10^\circ, 20^\circ, 30^\circ, 45^\circ$. Then, for each angle defined (except for $\theta = 0^\circ$), two measures were made rotating around the $y$ axis $\varphi = 0^\circ, 45^\circ$.   
\end{itemize}

@@

\begin{itemize}
\item Starting position: $z$ axis pointing ``up'': 9 measures were made combining two rotations. First, rotating around the $y$ axis: $\phi =0^\circ, -10^\circ, -20^\circ, -30^\circ, -45^\circ$. Then, for each angle defined (except for $\phi = 0^\circ$), two measures were made rotating around the $z$ axis $\theta = 0^\circ, 45^\circ$.   \end{itemize}

@@

First of all, the platform was attached to a wooden cube. This allows to perform $90^\circ$ rotations. Having an horizontal surface, measures with the gravity vector aligned to any of three axis, can be easily taken. The horizontal surface was assured using a three leg adjustable table (see Figure \refp{fig:mesa}). In addition this table allows us to perform rotations of known angles using a scaled semicircle and a pendulum as it is shown also in Figure \refp{fig:mesa}. The rotations over the second axis were made using a carpenter's square, therefore a proper $45^\circ$ rotation is achieved.\\

@@

Each measure was performed averaging 1934 samples, taken in less than 20 seconds.\\

@@

In this work it is also proposed to implement a temperature adjustment. The sensors are exposed to the operating temperature of the system, and it is very common that this temperature is different from the calibration temperature. The thermometer used in this work is the internal thermometer of the IMU, which indicates very precisely the operating temperature of the sensor. Sensors based in MEMS technology are sensitive to such variations. The variation of the measures is critical in some applications. In INS two of the Euler angles are usually obtained from the accelerometer, therefore if the measures are not certain the stability of the system cannot be guaranteed.\\

@@

The conclusion of this sum up information is that the variations of the temperature do not produce main changes on the gains of the sensors, yet the offsets are modified. Thus, the following temperature adjust is considered:

@@

In equation \refp{eq:temp} $\mathbf{b}_{s0}$ is the offset vector obtained in the static calibration, $T_0$ is the ambiance temperature in that calibration, $T$ is the working temperature of the system and $\boldsymbol{\alpha}_s$ is the parameter that is needed to know to complete the process.\\

@@

\begin{equation}
\boldsymbol{\alpha}_s = \arg \min_{\boldsymbol{\alpha}_s} \lbrace \sum_{k=1}^N ||\mathbf{s}_i^p - \mathbf{T}_{s0}^p(\mathbf{K_{s0}})^{-1}(\tilde{\mathbf{s}}_i^s-\mathbf{b}_s(T))||^2 \rbrace
\label{eq:calib_temp}
\end{equation}

In equation \refp{eq:calib_temp}, $N = 22740$\footnote{This number is not needed to be this big, yet all the data of the cooling process was used (see figure \ref{fig:bajada}).} is the number of samples took, $\mathbf{T}_{s0}^p$, $\mathbf{K_{s0}}$ are the matrix obtained in the static parameter calibration (ambiance temperature) and $\mathbf{b}_s(T)$ is the vector defined in \refp{eq:temp}. This last vector includes the variable to be estimated.\\

@@

It is interesting to compare the values obtained with the theoretical values of each parameter. As can be seen, comparing the vector obtained with the seed, the values of the gains and the rotations are similar to what is declared in the datasheets. Furthermore, the offset values are also consistent with the information of the datasheet, yet this is not a straightforward conclusion, thus the following analysis is presented. In \cite{bib:acc_data} is declared that the $0g$ output is $\pm 150 mg$ for axes $x$ and $y$ and $\pm 250mg$ for axis $z$. This correspond to offsets of $39$ bits maximum for $x$ and $y$, and $64$ for $z$. Therefore, can concluded that the results obtained are consistent with what is declared in the datasheets.

@@

The mean error obtained correspond to less that a bit of error and the standard deviation to a bit and a half. Therefore can concluded that a very good calibration has been achieved for the static parameters of the accelerometer.\\

@@
